A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-01-16 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp.tex

\begin{itemize}
\item Exploit the discovery of the Higgs boson as a precision tool
  for investigating Standard Model (SM) and Beyond the Standard Model
  (BSM) physics.
\item
  Etudy the decays of $b$- and $c$-hadrons, and tau leptons, in the search
  for manifestations of BSM physics, and investigate
  matter-antimatter differences.
\item
  Search for signatures of dark matter.
\item
  Probe neutrino oscillations and masses.
\item
  Study the Quark Gluon Plasma state of matter in heavy-ion collisions.
\item
  Explore the unknown.
\end{itemize}

>>>>

\begin{itemize}
\item Exploit the discovery of the Higgs boson as a precision tool
  for investigating Standard Model (SM) and Beyond the Standard Model
  (BSM) physics.
\item
  Study the decays of $b$- and $c$-hadrons, and tau leptons, in the search
  for manifestations of BSM physics, and investigate
  matter-antimatter differences.
\item
  Search for signatures of dark matter.
\item
  Probe neutrino oscillations and masses.
\item
  Study the Quark Gluon Plasma state of matter in heavy-ion collisions.
\item
  Explore the unknown.
\end{itemize}
